---
title: "Stat 450 Assignment 1"
author: "Jason Dong"
date: "January 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### A couple of sentences about myself

I am a fourth year Statistics major graduating this May. I currently work at Best Buy Corporate as a data analyst, primarily working on configuration management and inventory compilation. I used to play video games semi-professionally and also for UBC.

### My favorite equation

My favorite equation is the quadratic formula:

$x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$ 

where the general quadratic equation is

$ax^2+bx+c=0$

It is a simplistic method of finding the roots of the quadratic equation. Or in other terms, the x-values at which the parabola given by the quadratic equation crosses the x-axis. The quadratic formula is my favorite due to its many applications in real life, such as modelling the distance equation in physics, or price optimization in business.

### My favorite data set

I am very interested in what makes people happy. 
This dataset ranks countries based on a happiness score, which is dependent on information about GDP per Capita, life expectancy, freedom, generosity, and government corruption.


### First five rows of dataset
```{r}
library(knitr)
setwd("C:/Users/jasonxd/Downloads")
dat<-read.csv("2017.csv")
kable(dat[1:5,])
```

### Plot of happiness score against GDP per capita

```{r}
plot(dat$Happiness.Score, dat$Economy..GDP.per.Capita)
```